---
title: "lab_02"
author: "Derek Willis"
adapted by: "Daniel Trielli"
date: "2024-05-23"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load libraries and establish settings

```{r}
# Turn off scientific notation
options(scipen=999)

# Load the tidyverse. If you have not installed the tidyverse already, remove the # from the next line and run it first.  
# install.packages('tidyverse')
library(tidyverse)
library(lubridate)
```

## Load Data

Let's keep working with the UMD courses and Maryland campaign expense data we used in the pre_lab.

```{r}
umd_courses <- read_rds("data/umd_courses.rds")
maryland_expenses <- read_csv("data/maryland_expenses.csv")
```

## Answer questions

### **Q1** How many departments have offered the courses with "Climate" in the title and at least one seat? Which department has offered the most?

```{r}


climate_seats_1 <- umd_courses |> filter(str_detect(title, "Climate") & seats >= 1)

climate_seats_1 |>
  group_by(department) |>
  summarise(total_seats=sum(seats)) |>
  arrange(desc(total_seats))



umd_courses |> filter(str_detect(title, "Climate") & seats >= 1) |>  group_by(department) |>
  summarise(total_seats=sum(seats)) |>
  arrange(desc(total_seats))

```

**A1**

------------------------------------------------------------------------

### **Q2** Which departments have the most courses in the Fall 2023 term? And which departments in that term have at least one syllabus posted? How are the top departments different in each result? Where is Journalism in those results?

```{r}
umd_courses |>
  group_by(term, department) |>
  summarise(
    count_classes = n()
  ) |>
courses_2023 <- umd_courses |> filter(term > 202300) |>

head(courses_2023)

arrange_






```

**A2**

------------------------------------------------------------------------

### **Q3** Using the Maryland campaign expenses data, change the datatype of the expenditure_date column so that it is a date and not a chr. Then create a new column for the month based on expenditure_date. Then write code that shows total amount spent each month by Wes Moore's committee (you'll need to search the data to find the exact name). Write a sentence describing the pattern of spending over time.

```{r}
maryland_expenses <- maryland_expenses |> mutate(expenditure_date=mdy(expenditure_date))

head(maryland_expenses)

maryland_expenses |>
  mutate(month = floor_date(expenditure_date, "month")) |>
  #filter(committee_name == "Moore  Wes For Maryland") |>
  filter(str_detect(committee_name, "Moore")) |>
  group_by(month) |>
  summarise(total_amount = sum(amount)) |>
  arrange(desc(total_amount))
```

**A3**

------------------------------------------------------------------------

### **Q4** Using case_when(), create a column in the Maryland expenses data called `spending_location` indicating whether each record indicated money spent in Maryland or outside Maryland. For records that are in Maryland, make the new column's value "In-state" and for the others, make it "Out of state". Then write code that shows the total amount of money spent in each category and describe the results. You can do this in one statement or break it up into two statements (saving the new column to your dataframe).

```{r}
spending_location <- maryland_expenses |>
  mutate(
    state = case_when(
        str_detect(address, " Maryland ") ~ "In-state",
    .default = "out of state"
      )
  )
spending_location |>
  group_by(state) |>
  summarize(total = sum(amount)) |>
  arrange(desc(total))


```

**A4**

------------------------------------------------------------------------

### **Q5** Choose your own adventure: using either the UMD courses or campaign expenses data, ask and answer a question that is different than the previous ones. You can use one of the ones you provided in the pre_lab.

What is the sum of all advertising costs in 2023?

```{r}
maryland_expenses |>
  mutate(year(expenditure_date, "year")) |>
  group_by(year("202300")) |>
  summarise(total_amount = sum(amount)) |>
  arrange(desc(total_amount))


```

**A5**
