---
title: "lab_01"
author: "Derek Willis"
adapted by: "Daniel Trielli"
date: "2024-05-23"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Turn off scientific notation
options(scipen=999)
```

## About this lab

To complete this lab, you need to: \* run existing code as directed (look for **Task**). \* modify existing code as directed (look for **Task**). \* write code in empty codeblocks provided to answer questions included (look for **Q**). \* write out the answer in the form of a complete sentence in the space given (look for **A**). When you are finished, commit changes and push to your personal GitHub repo, then submit the URL to this document on ELMS.

Remember to add any new verbs or concepts to your class reference notebook!

## Load libraries and establish settings

**Task** Run the codeblock below to load the Tidyverse. To run the codeblock, hit the little green play button in the upper right corner of the gray area (the codeblock) below.

```{r}
# Load the tidyverse. If you have not installed the tidyverse already, remove the # from the next line and run it first.  
# install.packages('tidyverse')
library(tidyverse)
```

## Load Data

We're going to load the UMD courses data.

**Task** Run the codeblock below to load the data, which is contained in an RDS file.

```{r}
umd_courses <- read_rds("lab_01.rds")
```

## Answer questions

### **Q1** Which department has the highest mean (average) number of seats for its classes? You need to show the department with the highest average first. Which one is the most surprising/interesting to you?

```{r} 
umd_courses |>
  group_by(department) |>
  summarise(
    mean_seats = mean(seats),
  ) |>
  arrange(desc(mean_seats))

```

**A1**

------------------------------------------------------------------------

### **Q2** Find out the greatest number of times any individual class has been offered in our dataset. You must show the greatest number of classes first.

```{r} 
umd_courses |>
  group_by(title) |>
  summarise(
    max_syllabus_count = max(syllabus_count),
  ) |>
  arrange(desc(max_syllabus_count))

```






```
------------------------------------------------------------------------

**Q3** Count the number of courses for each instructor and department. Which instructor has taught the most?
``` {r}
umd_courses |>
  group_by(instructors, department) |>
  summarize(
    count_courses = n()
  ) |>
  arrange((count_courses))
```


**A3**
*This is the formula I got but does not let me run code*
------------------------------------------------------------------------

 **Q4** Given the results for Q3, what would have made it easier to find the answer? You don't have to know *how* to accomplish this; I want you to describe in words what would make the answer easier to see.

```{r}


**A4**

Arranging the code was fairly simple, the only trouble I had was organizing the instructors and department on the same line of code. I grouped them separarately at first and realized our strategies in the pre-lab. 
------------------------------------------------------------------------

### **Q5** Take one of the questions you listed in the final question of the pre_lab and try to answer it here in code. If you don't know how to fully answer it, write what code you can and describe in words what else you would need to do. If you got an answer, is it interesting?

```{r}
umd_courses |>
  group_by(instructors) |>
  summarise(
    count_instructors = count(instructors)
  ) |>
  arrange((count_instructors))


```

**A5**
The question I asked in my pre-lab was whether there is a way to determine a classes popularity in comparison to another. I attempted a number of strategies, and understood that the only way to figure that out was to find how often a class was taught and the number of students that repeatedly signed up. The data would have to be over a multi-year span and could not form a reasonable conslusion in one fiscal school year. 
